Modern Graph Generators: A Survey

### 2018-10-20 challenges.tex
Minor corrections

Considering the complex structure of graph data and the variety of applications
requiring highly specific types of graphs, the latter solution is difficult to
implement. A reasonable compromise can be found in a data generator which is
provided with sample graph data and is capable of automatic analysis of its
structural and value features in order to learn the complex parameters.

@@

Most of existing graph generators are focused on generating large graphs with realistic
structural characteristics focus principally on reproducing the degree
distribution and the clustering
coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
structural characteristics that one might be interested in reproducing for a large
graph, such as the diameter, the size of the largest connected component, or the
hierarchical community structure. Graph practitioners are highly interested in knowing
how other high-level structural characteristics affect the performance of graph
queries and graph algorithms. Hence, a compelling open challenge consists
of creating
graph generators that allow one to reproduce diverse structural characteristics
of the graphs along with large scale sizes.

@@

Most of existing graph generators also generate graphs that are either not labeled or
are specific to a given domain (e.g.  Social Networks). Graphs from different
domains have different schemas, structural characteristics, property
distributions, etc. which might have an impact on the performance of the
application under test. Thus, graph processing engine developers are asking for
generators or tools to flexibly and holistically generate multi-domain graphs  in a flexible and holistic manner, allowing to configure aspects
such as size, schemata, data distributions and other structural
characteristics such as degree distributions, clustering coefficients, and
so on.

@@

Concerning the former, analyzing and labelling structural networks is
deemed to be more difficult for graph datasets in the presence of noise.
Since denoising graph data is difficult to achieve, several machine learning
techniques have been adapted to work with noise (i.e. mislabeled
samples) or outliers, such as
imbalanced graph classification \cite{PanZ13} and
binary graph classification with positive and negative weights \cite{CheungSML16}.
Synthetic graph generators that take into account noisy and missing data
have been studied in \cite{NamataG10}, where graph identification is presented in
order to  model the inference of a cleaned output network from a
noisy input graph.
Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
generation of graph data and graph quality rules in order to assess the
effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The
corresponding graph quality rules are typically handcrafted by domain
experts, whereas an automatic generation of such rules along with the graph
data generation in tandem would be an interesting future challenge for the
community.

\subsection{Streaming Graph Generators}
Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
sensor pervasiveness and emerging IoT applications. These applications generate the data with high Velocity, one of the main 3V characteristics of big data applications~\cite{sakr2016big}. In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner. The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT. %Thus, there is a crucial need to tackle this aspect.
In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources. It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.

\subsection{Evolving Graph Data}
\label{sec:evolving}
As user requirements as well as environments change, most of the existing
applications naturally evolve over time, at least to some extent. This evolution
usually influences the structure of the data and consequently all the related
parts of the application (i.e., storage strategies, operations, indexes etc.).
In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}. They can be modelled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.

@@

\subsection{Multi-model Data}
With the dawn of Big Data and especially its variety aspect, new types of
database management systems have emerged. One of the most interesting ones
are the so-called \emph{multi-model databases} that enable to store and
thus query across structurally different data. There exist various types of
multi-model systems combining  distinct subsets of Big Data structures including graph data.
For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
implemented on the basis of an object DBMS currently supports graph, document,
key/value, and object models. Such type of DBMSs also needs a specific
data generator that would enable
to test new features and analyze efficiency of operations. However, since the
multi-model systems are in the context of Big Data are rather new, there exist only
a few benchmarks targeting multi-model DBMSs (such as
Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
with limited capabilities.

@@

Most of the existing work falls within the topic of graph generation with ``differential
privacy''~\cite{dwork2009differential} guarantees. More specifically, in
~\cite{wang2013preserving} the authors develop a differential privacy graph
generation approach based on the dK-graph generation
model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
Graph Model~\cite{LeskovecCKF05} in terms of the produced structural properties,
eventhough the results show that there is still room for improvement.

Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
and propose an `` edge local differential privacy'' based graph generation
method. The poposed method allows generating privacy preserving synthetic social
graphs wihtout the need of a centralized data curator, while preserving structural
properties more accurately than straw-hat methods such as Randomized
Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
Degree-based Graph Generation (which perturbates the original graph degrees
using the Laplace mechanism~\cite{dwork2009differential}). Again, eventhough the
proposed technique outperforms the baselines, the results show that there is
still room for improvement in terms of the structural properties of the
generated graph.

>>>>

Considering the complex structure of graph data and the variety of applications
requiring highly specific types of graphs, the latter solution is difficult to
implement. A reasonable compromise can be found in a data generator which is
provided with sample graph data and is capable of automatic analysis of its
structural and value features in order to learn the complex parameters. We could see this type approach in some cases, such as Semantic Web generators LBBM or DBPSB.

@@

Most of existing graph generators are focused on generating large graphs with realistic
structural characteristics and focus principally on reproducing the degree
distribution and the clustering
coefficient~\cite{kolda2014scalable,edunov2016darwini}. However, there are other
structural characteristics that one might be interested in reproducing for a large
graph, such as the diameter, the size of the largest connected component, or the
hierarchical community structure. Graph practitioners are highly interested in knowing
how other high-level structural characteristics affect the performance of graph
queries and graph algorithms. Hence, a compelling open challenge consists
of creating
graph generators that allow one to reproduce diverse structural characteristics
of the graphs along with large scale sizes.

@@

Most of existing graph generators also generate graphs that are either not labeled or
are specific to a given domain (e.g.  social networks). Graphs from different
domains have different schemas, structural characteristics, property
distributions, etc. which might have an impact on the performance of the
application under test. Thus, graph processing engine developers are asking for
generators or tools to generate multi-domain graphs  in a flexible and holistic manner, allowing to configure aspects
such as size, schemata, data distributions and other structural
characteristics such as degree distributions, clustering coefficients, and
so on.

@@

Concerning the former, analyzing and labeling structural networks is
deemed to be more difficult for graph datasets in the presence of noise.
Since de-noising graph data is difficult to achieve, several machine learning
techniques have been adapted to work with noise (i.e. mislabeled
samples) or outliers, such as
imbalanced graph classification \cite{PanZ13} and
binary graph classification with positive and negative weights \cite{CheungSML16}.
Synthetic graph generators that take into account noisy and missing data
have been studied in \cite{NamataG10}, where graph identification is presented in
order to  model the inference of a cleaned output network from a
noisy input graph.
Concerning the latter, data quality techniques handling graph data are recently considering ad-hoc
generation of graph data and graph quality rules in order to assess the
effectiveness of error detection and data repairing algorithms \cite{FanWX16a,AriouaB18}. The
corresponding graph quality rules are typically handcrafted by domain
experts, whereas an automatic generation of such rules along with the graph
data generation in tandem would be an interesting future challenge for the
community.

\subsection{Streaming Graph Generators}
Stream computing is a new paradigm that is necessitated by various modern data generation scenarios such as the ubiquity of mobile devices, location services,
sensor pervasiveness and emerging IoT applications. These applications generate the data with high Velocity, one of the main 3V characteristics of Big Data applications~\cite{sakr2016big}. In most of these high speed data generation scenarios, various objects are connected together with different relations and data exchanges  in a graph-structured manner. The Semantic Web community has been considering the aspect of implementing streaming RDF generator and benchmarks, however, there is still a clear lack on considering this aspect in other important and timely domains such as IoT. %Thus, there is a crucial need to tackle this aspect.
In addition, graph streaming generators should  consider some specific aspects for the stream processing domains such as the out-of-order handling (late arrivals)~\cite{li2008out} and the variety in the schemas and formats of the different data streaming sources. It is also recommended for the streaming graph generators to support the distributed environment as this is the most common scenario for such type of applications.

\subsection{Evolving Graph Data}
\label{sec:evolving}
As user requirements as well as environments change, most of the existing
applications naturally evolve over time, at least to some extent. This evolution
usually influences the structure of the data and consequently all the related
parts of the application (i.e., storage strategies, operations, indexes etc.).
In the world of graph data such graphs that change with time are denoted as \emph{evolving}, \emph{temporal}, \emph{dynamic}, or \emph{time-varying}. They can be modeled as labeled graphs, where the labels capture some measure of time~\cite{Michail2015}.

@@

\subsection{Multi-model Data}
With the dawn of Big Data and especially its Variety, another key 3V characteristic, new types of
database management systems have emerged. One of the most interesting ones
are the so-called \emph{multi-model databases} that enable to store and
thus query across structurally different data. There exist various types of
multi-model systems combining  distinct subsets of Big Data structures including graph data.
For example, OrientDB\footnote{\url{http://orientdb.com/orientdb/}} which was
implemented on the basis of an object DBMS currently supports graph, document,
key/value, and object models. Such type of DBMSs also needs a specific
data generator that would enable
to test new features and analyze efficiency of operations. However, since the
multi-model systems are in the context of Big Data rather new, there exist only
a few benchmarks targeting multi-model DBMSs (such as
Bigframe~\cite{journals/pvldb/KunjirKB14} or UniBench~\cite{conf/cidr/lu17})
with limited capabilities.

@@

Most of the existing work falls within the topic of graph generation with ``differential
privacy''~\cite{dwork2009differential} guarantees. More specifically, in
~\cite{wang2013preserving} the authors develop a differential privacy graph
generation approach based on the dK-graph generation
model~\cite{mahadevan2006systematic} that outperforms the Stochastic Kronecker
Graph Model~\cite{Leskovec:2005:RMT:2101235.2101254} in terms of the produced structural properties,
even though the results show that there is still room for improvement.

Following this line of research, recent work~\cite{qin2017generating} extends the notion of differential privacy
and propose an ``edge local differential privacy'' based graph generation
method. The proposed method allows generating privacy preserving synthetic social
graphs without the need of a centralized data curator, while preserving structural
properties more accurately than straw-hat methods such as Randomized
Neighbor Lists (based on randomized response~\cite{dwork2014algorithmic}) and
Degree-based Graph Generation (which perturbates the original graph degrees
using the Laplace mechanism~\cite{dwork2009differential}). Again, even though the
proposed technique outperforms the baselines, the results show that there is
still room for improvement in terms of the structural properties of the
generated graph.

### 2018-10-20 conclusion.tex
Minor corrections

Graph data occur in a vast amount of distinct applications, such as biology, chemistry, physics, computer science, or social sciences, to name just a few. Graphs form one of the most complex data structures requiring specific and usually sophisticated approaches for processing and analysis. The history of graph theory,  that started from when these structures and their respective algorithms were studied can be traced back to the 18th century.

>>>>

Graph data occur in a vast amount of distinct applications, such as biology, chemistry, physics, computer science, or social sciences, to name just a few. Graphs form one of the most complex data structures requiring specific and usually sophisticated approaches for processing and analysis. The history of graph theory,  that started from when these structures and their respective algorithms were studied, can be traced back to the 18th century.
